### 2015-02-05 paper_40_mpi.tex
finished tables for 3 focus areas and questions for software analytics

How much better is my model performing than a naive strategy, such as guessing? & MPI 
provides consistency which may not exist without it.  Therefore, MPI removes the 
guesswork of measuring a software development organization. \\
\myrowcolour%
How practically significant are the results? &  \\
How sensitive are the results to small changes in one or more of the inputs? & 
The question was extensively addressed in section \ref{sub:sensitivity}.  It appears MPI is
not overly sensitive to small changes in the inputs.\\

>>>>

How much better is my model performing than a naive strategy, such as guessing? & MPI 
provides consistency which may not exist without it.  Therefore, MPI removes the 
guesswork of measuring a software development organization. \\
\myrowcolour%
How practically significant are the results? & The MPI score is consistent
and easy to comprehend.  Thus comparison with past performance is quick 
and simple.  This is a significant advantage for software 
development organizations. \\
How sensitive are the results to small changes in one or more of the inputs? & 
The question was extensively addressed in section \ref{sub:sensitivity}.  It appears MPI is
not overly sensitive to small changes in the inputs.\\
